---
title: "Portfolio"
toc: true
toc-title: "On this page"
---

# Data Visualization Portfolio

This page highlights examples of reproducible data analysis and visualization workflows created using R and Quarto.

------------------------------------------------------------------------

## Carbon Emissions Visualization

The figure below demonstrates a simple greenhouse gas emissions trend analysis using R and ggplot2.

```{r}
#| label: fig-emissions
#| fig-cap: "Example greenhouse gas emissions trend"
#| warning: false
#| message: false

library(ggplot2)

emissions <- data.frame(
  Year = c(2019, 2020, 2021, 2022, 2023),
  Emissions = c(125, 118, 110, 97, 85)
)

ggplot(emissions, aes(x = Year, y = Emissions)) +
  geom_line(linewidth = 1.2, color = "#2C7FB8") +
  geom_point(size = 3, color = "#1B7837") +
  labs(
    x = "Year",
    y = "GHG Emissions (t CO2-eq)",
    title = "Greenhouse Gas Emissions Trend"
  ) +
  theme_minimal(base_size = 14)
```

------------------------------------------------------------------------

## Sustainability Summary Table

This section demonstrates simple data summarization using reproducible R workflows.

```{r}
#| warning: false
#| message: false

library(dplyr)

sustainability_data <- data.frame(
  Sector = c("Energy", "Agriculture", "Transportation", "Industry"),
  Reduction = c(32, 18, 24, 15)
)

sustainability_data %>%
  arrange(desc(Reduction))
```

------------------------------------------------------------------------

## Reproducible Workflow Example

The following code chunk demonstrates a basic reproducible workflow used in environmental data analysis.

::: {.callout-note collapse="true"}
## View R Code

```{r}
mean_emissions <- mean(emissions$Emissions)

paste(
  "Average emissions across all years:",
  round(mean_emissions, 2),
  "t CO2-eq"
)
```
:::

------------------------------------------------------------------------

## Technical Skills Demonstrated

- Reproducible reporting with Quarto
- Data visualization using ggplot2
- Data manipulation using dplyr
- Environmental data analysis workflows in R
- Dynamic document generation
